Is Google Translate Sexist? -- Assessing Gender Bias in Machine Translation

### 2017-12-25 paper/main.tex
Update main.tex
Updated caption for scatterplot figure

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/scatterplot-languages}
	\caption{Scatter plot of translated sentences' statistics. Each point (color coded according to its category) corresponds to a single occupation, of which the sex ratio and the percentage of gender neutral pronouns are averaged over all tested languages (Malay, Estonian, Finnish, Hungarian, Armenian, Japanese, Turkish, Yoruba, Basque, Swahili and Chinese).}
	\label{fig:scatterplot-languages}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{pictures/scatterplot-languages}
	\caption{Scatter plot of the translated sentences' statistics. Each point, corresponding to a single occupation, is positioned in the horizontal axis according to its sex ratio and in the vertical axis according to the frequency with which it is translated using gender neutral pronouns. Both quantities are averaged over all tested languages.}
	\label{fig:scatterplot-languages}
\end{figure}
